### 2015-03-10 ResearchNotes/Notes.Rmd
Added a few variables and did diagnosis on weights.

##Start Recoding HERE
summary(RECS$AGECDRYER)
summary(RECS$TVCOLOR)
summary(RECS$TVTYPE1)
summary(RECS$TVONWD1)
summary(RECS$NUMPC)
summary(RECS$TIMEON1)
summary(RECS$WELLPUMP)
summary(RECS$EQUIPM)
summary(RECS$FUELHEAT)
summary(RECS$EQUIPAGE)
summary(RECS$TEMPHOME)
summary(RECS$TEMPGONE)
summary(RECS$TEMPNITE)
summary(RECS$H2OTYPE1)
summary(RECS$FUELH2O)
summary(RECS$WHEATSIZ)
summary(RECS$WHEATAGE)
summary(RECS$AIRCOND)
summary(RECS$COOLTYPE)
summary(RECS$CENACHP)
summary(RECS$AGECENAC)
summary(RECS$USECENAC)
summary(RECS$TEMPHOMEAC)
summary(RECS$TEMPGONEAC)
summary(RECS$TEMPNITEAC)
summary(RECS$NUMBERAC)
summary(RECS$WWACAGE)
summary(RECS$ESWWAC)
summary(RECS$USEWWAC)
summary(RECS$SWIMPOOL)
summary(RECS$POOL)
summary(RECS$FUELPOOL)
summary(RECS$RECBATH)
summary(RECS$FUELTUB)
summary(RECS$TYPEGLASS)
summary(RECS$ELCOOL)
summary(RECS$ELWARM)
summary(RECS$ELWATER)

summary(RECS$ELFOOD)

@@

```
Checkign out the weight variable
```{r}
summary(RECS$NWEIGHT)

```
Looks like it is the number of equivelent HH in population style.

@@

#And the clean up from importing from excell
HUD$pop<-as.numeric(gsub(",","",HUD$pop))
summary(HUD)
```

```{r}
as.numeric(HUD$Pop)
```

>>>>

##Start Recoding HERE
summary(RECS$AGECDRYER)
summary(RECS$TVCOLOR)
summary(RECS$TVTYPE1)
summary(RECS$TVONWD1)
summary(RECS$NUMPC)
summary(RECS$TIMEON1)
summary(RECS$WELLPUMP)
summary(RECS$EQUIPM)
summary(RECS$FUELHEAT)
summary(RECS$EQUIPAGE)
summary(RECS$TEMPHOME)
summary(RECS$TEMPGONE)
summary(RECS$TEMPNITE)
summary(RECS$H2OTYPE1)
summary(RECS$FUELH2O)
summary(RECS$WHEATSIZ)
summary(RECS$WHEATAGE)
summary(RECS$AIRCOND)
summary(RECS$COOLTYPE)
summary(RECS$CENACHP)
summary(RECS$AGECENAC)
summary(RECS$USECENAC)
summary(RECS$TEMPHOMEAC)
summary(RECS$TEMPGONEAC)
summary(RECS$TEMPNITEAC)
summary(RECS$NUMBERAC)
summary(RECS$WWACAGE)
summary(RECS$ESWWAC)
summary(RECS$USEWWAC)
summary(RECS$SWIMPOOL)

summary(RECS$POOL)

#Fuel used for pool
RECS$FUELPOOL<-revalue(as.factor(RECS$FUELPOOL),c("1"="NG","2"="LPG", "3"="FuelOil","4"="Kerosene", "5"="Elec","8"="Solar","21"="Other", "-2"=NA))
summary(RECS$FUELPOOL)

#Hot Tub used
RECS$RECBATH<-revalue(as.factor(RECS$RECBATH),c("0"=FALSE,"1"=TRUE))
summary(RECS$RECBATH)

#Hot tub fuel
RECS$FUELTUB<-revalue(as.factor(RECS$FUELTUB),c("1"="NG","2"="LPG", "3"="FuelOil","4"="Kerosene", "5"="Elec","8"="Solar","21"="Other", "-2"=NA))
summary(RECS$FUELTUB)

RECS$TYPEGLASS<-revalue(as.factor(RECS$TYPEGLASS),c("1"="SinglePane","2"="DoublePane", "3"="TriplePane", "-2"=NA))
summary(RECS$TYPEGLASS)

#Electricity used for cooling
RECS$ELCOOL<-revalue(as.factor(RECS$ELCOOL),c("0"=FALSE,"1"=TRUE))
summary(RECS$ELCOOL)

#Electricity used for space heating
RECS$ELWARM<-revalue(as.factor(RECS$ELWARM),c("0"=FALSE,"1"=TRUE))
summary(RECS$ELWARM)

#Electricity used for water heating
RECS$ELWATER<-revalue(as.factor(RECS$ELWATER),c("0"=FALSE,"1"=TRUE))
summary(RECS$ELWATER)

#Electricity used for cooking
RECS$ELFOOD<-revalue(as.factor(RECS$ELFOOD),c("0"=FALSE,"1"=TRUE))
summary(RECS$ELFOOD)

@@

```
Checkign out the weight variable
```{r}
summary(RECS$NWEIGHT)
plot(hist(RECS$NWEIGHT))
```
Looks like it is the number of equivelent HH in population style.

the weights are a little odd, too large differences.  Investigate the top end to find.
```{r}
summary(RECS[RECS$NWEIGHT>40000,])

```
They are very poor.  Solution is to drop the ones with weights greater than 40K.  TODO

@@

#And the clean up from importing from excell
HUD$pop<-as.numeric(gsub(",","",HUD$pop))
HUD$reportablen<-as.factor(HUD$reportablen)
summary(HUD)
```
# Some Ideas on what matters
```{r}

table(RECS$UR, RECS$RENTHELP)

table(RECS$TYPEHUQ,RECS$KOWNRENT)
#Dump the houses that are free

boxplot(RECS$TOTSQFT_EN~RECS$REPORTABLE_DOMAIN )

boxplot(RECS$TOTSQFT_EN~RECS$EDUCATION )
boxplot(RECS$TOTSQFT_EN~RECS$UR )

table(RECS$EDUCATION)

table(RECS$UR,RECS$Householder_Race)
```
